---
title: "Crappy Politics of Australia"
author: "Teun van Gils, Lucie Kattenbroek, Joska de Langen, Joris Vincent"
date: "2025-01-24"
institute: "University College Utrecht"
format: 
  revealjs:
    incremental: true   
    theme: "moon"
editor: visual
---

## Australia

-   It's a country
    -   allegedly (LaTeX Lovers, 2025)
-   They have elections
    -   Next ones must be held before May 2025
-   Can you vote in them?
    -   Who knows...
-   How should you make your electoral decision?

. . .

**Trust your gut**

## Trust your gut

Gut-brain axis

-   gut-microbiome affects brain chemistry, possible cognition
-   has traditionally been ignored in research on decision-making
-   may actually be involved in important decisions such as voting

. . . 

**does one use their gut to make electoral decisions?**

## *"Ask not what your country can do for you,*\n but what you can doo-doo for your country" - JFK

Scenario sketch:

-   You want to vote in the 2025 Australian election
-   But you have not made up your gut yet
-   So you find a public restroom
-   Let your gut decide
-   Go vote.

. . . 

**how would you vote?**

## What are the voting patterns related to public toilets in Australia?

## Pipeline Overview {.smaller}

<!-- visualise pipeline using mermaid -->

```{mermaid}
flowchart LR
  A[Public toilets] --> B[NearestToiletPP]
  C[Polling places] --> D[PPLeanings]
  C --> B
  B --> E[ToiletLeanings]
  D --> E
```

::::: {columns}
::: {.column width="50%"}
1.  Find a toilet
    -   24175 public toilets in Australia
    -   dataset info goes here...
    -   with their properties
2.  Go PP
    -   find nearest polling place to each toilet
    -   out of polling places (8479) used in the 2022 recent election
    -   provided by Australian Election Committee Tally Room
    
:::

::: {.column width="50%"}
3.  Leaning PP
    -   For each polling place, determine political leaning
    -   Amount of votes per party
    -   Classify parties as left/right (progressive/conservative)
    -   Determine (proportion of) votes per leaning, for each polling place
4.  Leaning Toilets
    -   Combine toilet & PP
:::
:::::

## Code

When you click the **Render** button a presentation will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

```{r}
library(tidyverse)

read_csv('data/toilet_leanings.csv') |>
    pivot_longer(cols=c(
        "Male", "Female", "AllGender", "Unisex",
        "AdultChange", "BabyChange", "BabyCareRoom", "Accessible",
        "SanitaryDisposal", "MensPadDisposal", "Shower", 
        "DrinkingWater", "Parking"
    ), names_to = "Property", values_to = "Present") |>
    group_by(Property, Present) |>
    summarise(
        leaning = mean(Leaning, na.rm = TRUE)
    ) |>
    filter(Present) |>
    ggplot() +
        aes(angle = - leaning * 360, color = leaning) +
        geom_text(label = '🚽', x = 0.5, y = 0.5, size = 30) +
        facet_wrap(~ fct_reorder(Property, leaning)) +
        scale_color_gradient2(low = "blue", mid = "black", high = "red") +
        theme(legend.position = "none")
```